---
title: "Process Boston Data to find most Influencing Features"
---
# * output: html_notebook
# * Author: shasibhusan
# * Read required Packages 

```{r}
library(corrplot)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(car)
```

# * Below are features types and use
# * crime per capita crime rate by town.
# * zn      proportion of residential land zoned for lots over 25,000 sq.ft.
# * indus   proportion of non-retail business acres per town.
# * chas    Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
# * nox     nitrogen oxides concentration (parts per 10 million).
# * rm      average number of rooms per dwelling.
# * age     proportion of owner-occupied units built prior to 1940.
# * dis     weighted mean of distances to five Boston employment centres.
# * rad     index of accessibility to radial highways.
# * tax     full-value property-tax rate per \$10,000.
# * ptratio pupil-teacher ratio by town.
# * black   1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.
# * lstat   lower status of the population (percent).
# * medv    median value of owner-occupied homes in \$1000s.
# * Read Boston data Set using Mass Pkg

```{r}
data(package='MASS')
data('Boston')
str(Boston)
## Setting any name change
names(Boston) = c('crim','zn','indus','chas','nox','rm','age','dis','rad','tax','ptratio','black','lstat','medv')
attach(Boston)
```

# * Find multi collinearity

```{r}

M = cor(Boston)
head(round(M,2))
cor.mtest =function(mat) {
  mat = as.matrix(mat)
  n = ncol(mat)
  p.mat= matrix(NA, n, n)
  diag(p.mat) = 0
  
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      # loopval =   paste('i=',i,'j=',j)
      # print(loopval)
      tmp = cor.test(mat[, i], mat[, j])
      p.mat[i, j] = p.mat[j, i] = tmp$p.value
    }
  }
  colnames(p.mat) = rownames(p.mat) = colnames(mat)
  p.mat
}
p.mat=cor.mtest(Boston)

corrplot(M, method = 'circle')

```
```{r}
# Leave blank on no significant coefficient
corrplot(M, type="upper", order="hclust", p.mat = p.mat, sig.level = 0.01, insig = "blank")
```
# * Linear Regression Model building
# * Running model and checking for significant *** features
```{r}
str(Boston)
# Bulding with all attributes, to find most influecning feature
salesLM_all = lm(medv ~ zn+nox+rm+dis+rad+ptratio+black ,data = Boston)
summary(salesLM_all)
```

# * analysing data with different features and combinations
```{r}

salesLM_nox = lm(medv ~ nox ,data = Boston)
summary(salesLM_nox)

salesLM_rm = lm(medv ~ rm , data = Boston)
summary(salesLM_rm)

salesLM_nox_rm = lm(medv  ~ nox + rm+ nox:rm, data = Boston)
summary(salesLM_nox_rm)
```

# * after removing un significant features building final model with below features
# * nox,rm,dis,ptratio,black shows strong co relation.

```{r}
salesLM_all_after_cleanUP = lm(medv ~ nox+rm+dis+ptratio+black ,data = Boston)
summary(salesLM_all_after_cleanUP)

```

# * Vif The variance inflation factor (VIF) quantifies the extent of correlation between one predictor and the other predictors in a model.

```{r}

vif(salesLM_all)
```


```{r}
```
```{r}
vif(salesLM_all_after_cleanUP)
```


